Katherine Analysis

### 2018-03-19 Katherine Analysis.Rmd
Commit work

  * File creation date: `r Sys.Date()`
  * `r R.version.string`
  * `tidyverse` package version: `r packageVersion("tidyverse")`
  * `lme4` package version `r packageVersion("lme4")`
  * `MASS` package version `r packageVersion("MASS")`
  * `MuMIn` package version `r packageVersion("MuMIn")`
  * `emmeans` package version `r packageVersion("emmeans")`
  * `boot` package version `r packageVersion("boot")`
  * `brms` package version `r packageVersion("brms")`
  * `loo` package version `r packageVersion("loo")`
  * `fitdistrplus` package version `r packageVersion("fitdistrplus")`
  * `mefa` package version `r packageVersion("mefa")`
  * `library(devtools)` and `install_github("vqv/ggbiplot")` package version `r packageVersion("ggbiplot")`
  * `vegan` package version `r packageVersion("vegan")`
  * `glmmADMB` package version `r packageVersion("glmmADMB")`
  * `car` package version `r packageVersion("car")`
  * `factoextra` package version `r packageVersion("factoextra")`
  * `pvclust` package version `r packageVersion("pvclust")`

@@

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)
library(mefa)
library(ggbiplot)
library(pvclust)
library(vegan)
library(ggbiplot)
library(factoextra)
library(glmmADMB)
library(car)
```

@@

```{r echo=F}
# theme_simple() a homemade function from the Colautti lab (2017) to standardize figures
theme_simple <- function (base_size = 16, base_family = "") {
  theme_classic(base_size = base_size, base_family = base_family) %+replace%
    theme(
      axis.text = element_text(colour = "black"),
      axis.title.x = element_text(size=18),
      axis.text.x = element_text(size=16, face= "italic"),
      axis.title.y = element_text(size=18, angle=90), 
      axis.text.y = element_text(size=16),
      axis.ticks = element_blank(),
      panel.background = element_rect(fill="white"),
      panel.border = element_blank(),
      plot.title=element_text(face="bold", size=24)
      #      legend.position="none"
    )
}
```

@@

```{r echo=F}
overdisp_fun <- function(model) {
  ## number of variance parameters in an n-by-n variance-covariance matrix
  vpars <- function(m) {
    nrow(m) * (nrow(m) + 1)/2
  }
  # The next two lines calculate the residual degrees of freedom
  model.df <- sum(sapply(VarCorr(model), vpars)) + length(fixef(model))
  rdf <- nrow(model.frame(model)) - model.df
  # extracts the Pearson residuals
  rp <- residuals(model, type = "pearson")
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  # Generates a p-value. If less than 0.05, the data are overdispersed.
  pval <- pchisq(Pearson.chisq, df = rdf, lower.tail = FALSE)
  c(chisq = Pearson.chisq, ratio = prat, rdf = rdf, p = pval)
}
```

@@

fdata$None.Myc <- as.factor(fdata$None.Myc)
fdata$Herbivory <- as.factor(fdata$Herbivory)
fdata$Mycorrhiza <- as.factor(fdata$Mycorrhiza)
fdata$Lesion <- as.factor(fdata$Lesion)
fdata$None.Herb <- as.factor(fdata$None.Herb)
fdata$None.Path <- as.factor(fdata$None.Path)
summary(fdata)

#### Gather ####
length(unique(fdata$indiv2))
Cross<- data.frame(c(rep(1:100, times=225)))
fdatac <- cbind(fdata,Cross)
colnames(fdatac)[11]<-"cross"
fdatac %>% gather(Trait, Value, c(4,6,7)) -> fdata_gather # The warning is an inconsequential bug from tidyverse (https://github.com/tidyverse/tidyr/issues/386)
fdata_gather$Value<-as.numeric(fdata_gather$Value)
fdata_gather$Trait<-as.factor(fdata_gather$Trait)
fdata_gather <- fdata_gather[,-c(2:4)]
```

@@

ndata<-cbind(indiv,tdata)
ndata<-ndata[,-c(2,3,4,9,14,17:37)]
ndata$None.Path<-as.integer(ndata$None.Path)
ndata$None.Myc<-as.integer(ndata$None.Myc)

@@

FloristicSurvey$Population<-as.factor(FloristicSurvey$Population) # Make the population a factor and not an interger
FloristicSurvey[is.na(FloristicSurvey)] <- 0
sum(row.has.na <- apply(FloristicSurvey, 1, function(x){any(is.na(x))}))

@@

### Linear discriminate analysis
```{r}
# Discriminant function analysis is used (general LDA format) because i have a cat. dependent and a binary independent. (it needs binary or continuous!)
# you might have to bin covers because it only works with categorical, so 0-5% none, 6-40 low etc.
FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,25,50,75,100), labels = c("None to Low","Medium", "High", "Overtaken"))
table(FloristicSurvey$GM_Coverage_category)
# [0-20] None
# ]20-40] low
# ]40-60] Medium 
# ]60-80] high
# ]80-100] Overtaken
```

```{r}
#LDA
FloristicSurveysmall<-data.frame(FloristicSurvey[,4:56])
# Linear discriminant function analysis

FloristicSurveysmall <- FloristicSurveysmall[,-c(42,45)] 
FloristicSurveyLDA <- lda(GM_Coverage_category ~., data=FloristicSurveysmall)
# Extract scaling vectors
scalvec<-data.frame(FloristicSurveyLDA$scaling)
# Extract predictions
FloristicSurveyLDAval <- data.frame(predict(FloristicSurveyLDA)$x)

# Plot results
ggplot(data=FloristicSurveyLDAval,aes(x=LD1, y=LD2, group=FloristicSurveysmall$GM_Coverage_category))+
  stat_ellipse(geom="polygon",aes(colour=FloristicSurveysmall$GM_Coverage_category),fill=NA,size=1.2,alpha=0.3)+
  stat_ellipse(geom="polygon",aes(fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=1.2,alpha=0.3)+
  geom_point(aes(shape=FloristicSurveysmall$GM_Coverage_category,fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=I(4),alpha=I(0.8))+
  xlab("LD Axis 1")+ylab("LD Axis 2")+theme_simple() +
  theme(legend.title=element_blank())

#test significance of axis
anova(lm(FloristicSurveyLDAval$LD1~FloristicSurveysmall$GM_Coverage_category))
anova(lm(FloristicSurveyLDAval$LD2~FloristicSurveysmall$GM_Coverage_category))

#LDA WITHOUT A. PETIOLATA
FloristicSurveysmall<-data.frame(FloristicSurvey[,4:56])
# Linear discriminant function analysis
FloristicSurveysmall[10]<-NULL
FloristicSurveysmall[c(41,44)] <- NULL 
FloristicSurveyLDA<-lda(GM_Coverage_category ~ ., data=FloristicSurveysmall)
# Extract scaling vectors
scalvec<-data.frame(FloristicSurveyLDA$scaling)
# Extract predictions
FloristicSurveyLDAval <- data.frame(predict(FloristicSurveyLDA)$x)

# Plot results
LDA_of_Floristic_Composition<-ggplot(data=FloristicSurveyLDAval,aes(x=LD1,y=LD2,group=FloristicSurveysmall$GM_Coverage_category))+
  stat_ellipse(geom="polygon",aes(colour=FloristicSurveysmall$GM_Coverage_category),fill=NA,size=1.2,alpha=0.3)+
  stat_ellipse(geom="polygon",aes(fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=1.2,alpha=0.3)+
  geom_point(aes(shape=FloristicSurveysmall$GM_Coverage_category,fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=I(4),alpha=I(0.8))+
  xlab("LD Axis 1")+ylab("LD Axis 2")+
  ggtitle("LDA of Floristic Composition \n in a Garlic Mustard Population")+
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_color_manual(values=c("green3"," blue3","orange3","red3"))+ scale_fill_manual(values=c("green3","blue3","orange3","red3"))
ggsave(file="LDA_of_Floristic_Composition.epx", plot=LDA_of_Floristic_Composition, width=10, height=8)

#test significance of axis
anova(lm(FloristicSurveyLDAval$LD1~FloristicSurveysmall$GM_Coverage_category))
anova(lm(FloristicSurveyLDAval$LD2~FloristicSurveysmall$GM_Coverage_category))
```

@@

## finally plotting.
mult <- 1 #multiplier for the arrows and text for envfit below. You can change this and then rerun the plot command.
ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, color=df_ell.FSurvey.GM_coverage$GM_coverage))+ 
    geom_point( aes(color = FloristicSurvey.NMDS.data$GM_Coverage), size = 1)+ 
    scale_color_manual(values = c(14,5,19,2))+ 
    coord_cartesian(xlim = c(-1,1.5))+
  theme_simple()+ guides(color=guide_legend("Garlic Mustard Coverage"))+
  ggtitle("LDA of Floristic Composition \n in a Garlic Mustard Population")+
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_color_manual(values=c("green3"," blue3","orange3","red3"))+ scale_fill_manual(values=c("green3","blue3","orange3","red3"))
ggsave(file="LDA_of_Floristic_Composition.epx", plot=LDA_of_Floristic_Composition, width=10, height=8)
```

### PCA
```{r}
FloristicSurvey.pca <- prcomp(FloristicSurvey[,4:(ncol(FloristicSurvey)-1)],center = TRUE) 
summary(FloristicSurvey.pca)
factoextra::fviz_eig(FloristicSurvey.pca,addlabels=TRUE,hjust = -0.3)+theme_simple()
library(ggfortify)
autoplot(FloristicSurvey.pca, data = FloristicSurvey, colour = "GM_Coverage_category", label.size = 3)+theme_simple()
round(FloristicSurvey.pca$sdev^2/sum(FloristicSurvey.pca$sdev^2)*100,2)
# About 25% explained by my first 2 eigenvectors. 50% by the first 6.
```

### Modeling (redundancy analysis)
species comp ~ GMcov * pop + soil characteristics inside and outside as covariates? 
```{r}

@@

# Redundancy analysis
sp.comp <- FloristicSurvey[,4:(length(FloristicSurvey))]
var <- FloristicSurvey[,1:3]
var$Quadrat <- as.character(var$Quadrat)
for(i in 1:length(var$Quadrat))if(var$Population[i] == "7"){
  var$Quadrat[i]<-paste("7",var$Quadrat[i],sep="")
}else if(var$Population[i] == "3"){
  var$Quadrat[i]<-paste("3",var$Quadrat[i],sep="")
}else if(var$Population[i] == "14"){
  var$Quadrat[i]<-paste("14",var$Quadrat[i],sep="")
}else if(var$Population[i] == "13"){
  var$Quadrat[i]<-paste("13",var$Quadrat[i],sep="")
}else if(var$Population[i] == "1"){
  var$Quadrat[i]<-paste("1",var$Quadrat[i],sep="")
}

var$Population <- as.factor(var$Population)
var$GM_Coverage<-as.numeric(var$GM_Coverage)
sp.comp<-as.matrix(sp.comp)

formulaRDA <- rda(sp.comp ~ GM_Coverage + Condition(Population) , data=var)

formulaRDA <- rda(sp.comp ~ GM_Coverage , data=var)
head(summary(formulaRDA))
RsquareAdj(formulaRDA)
plot(formulaRDA, scaling = 2)
anova.cca(formulaRDA,step=1000)
anova.cca(formulaRDA,by="axis", step=1000)

@@

*Note that I redid this with GM_coverage_catogory and i didnt find ANY significance!

@@

par(mfrow=c(2,2))
ggplot(Soil_characteristics, aes(Location,Agg_stability,fill=Location))+ geom_boxplot() +
  theme_simple()
ggplot(Soil_characteristics, aes(Location,pH,fill=Location))+ geom_boxplot() +
  theme_simple()
ggplot(Soil_characteristics, aes(Location,C_percent,fill=Location))+ geom_boxplot() +
  theme_simple()
ggplot(Soil_characteristics, aes(Location,N_percent,fill=Location))+ geom_boxplot() +
  theme_simple()
Soil_characteristics$Population<-as.factor(Soil_characteristics$Population)

GLMER_soil <- glmer(Location~scale(Agg_stability)*scale(C_percent)*scale(N_percent)+(1|Population),family=binomial(link='logit'),data=Soil_characteristics)
summary(GLMER_soil)
options(na.action = "na.fail")
dredge(GLMER_soil) 
# A model with nothing is best...
```

@@

ggplot(fdat_ind,aes(species,Mycorrhiza,colour=loc))+geom_boxplot()+theme_simple()
ggplot(fdat_ind,aes(pop,Mycorrhiza,colour=loc))+geom_boxplot()+theme_simple()
```

>>>>

  * File creation date: `r Sys.Date()`
  * `r R.version.string`
  * `tidyverse` package version: `r packageVersion("tidyverse")`
  * `lme4` package version `r packageVersion("lme4")`
  * `MASS` package version `r packageVersion("MASS")`
  * `MuMIn` package version `r packageVersion("MuMIn")`
  * `emmeans` package version `r packageVersion("emmeans")`
  * `boot` package version `r packageVersion("boot")`
  * `brms` package version `r packageVersion("brms")`
  * `loo` package version `r packageVersion("loo")`
  * `fitdistrplus` package version `r packageVersion("fitdistrplus")`
  * `mefa` package version `r packageVersion("mefa")`
  * `library(devtools)` and `install_github("vqv/ggbiplot")` package version `r packageVersion("ggbiplot")`
  * `vegan` package version `r packageVersion("vegan")`
  * `glmmADMB` package version `r packageVersion("glmmADMB")`
  * `car` package version `r packageVersion("car")`
  * `factoextra` package version `r packageVersion("factoextra")`
  * `pvclust` package version `r packageVersion("pvclust")`
  * `effects` package version `r packageVersion("effects")`
  * `coefplot2` package version `r packageVersion("coefplot2")`
  * `bbmle` package version `r packageVersion("bbmle")`
  * `gridExtra` package version `r packageVersion("gridExtra")`

@@

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)
library(mefa)
library(ggbiplot)
library(pvclust)
library(vegan)
library(ggbiplot)
library(factoextra)
library(glmmADMB)
library(car)
library(effects)
library(coefplot2)
library(bbmle)
library(gridExtra)
library(corrplot)
library(ade4)
```

@@

```{r echo=F}
# theme_simple() a homemade function from the Colautti lab (2017) to standardize figures
theme_simple <- function (base_size = 16, base_family = "") {
  theme_classic(base_size = base_size, base_family = base_family) %+replace%
    theme(
      axis.text = element_text(colour = "black"),
      axis.title.x = element_text(size=18),
      axis.text.x = element_text(size=16, face= "italic"),
      axis.title.y = element_text(size=18, angle=90), 
      axis.text.y = element_text(size=16),
      axis.ticks = element_blank(),
      panel.background = element_rect(fill="white"),
      panel.border = element_blank(),
      plot.title=element_text(face="bold", size=24)
      #      legend.position="none"
    )
}

grid_arrange_shared_legend <-
  function(...,
           ncol = length(list(...)),
           nrow = 1,
           position = c("bottom", "right")) {

    plots <- list(...)
    position <- match.arg(position)
    g <-
      ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
    legend <- g[[which(sapply(g, function(x)
      x$name) == "guide-box")]]
    lheight <- sum(legend$height)
    lwidth <- sum(legend$width)
    gl <- lapply(plots, function(x)
      x + theme(legend.position = "none"))
    gl <- c(gl, ncol = ncol, nrow = nrow)

    combined <- switch(
      position,
      "bottom" = arrangeGrob(
        do.call(arrangeGrob, gl),
        legend,
        ncol = 1,
        heights = grid::unit.c(unit(1, "npc") - lheight, lheight)
      ),
      "right" = arrangeGrob(
        do.call(arrangeGrob, gl),
        legend,
        ncol = 2,
        widths = grid::unit.c(unit(1, "npc") - lwidth, lwidth)
      )
    )

    grid::grid.newpage()
    grid::grid.draw(combined)

    # return gtable invisibly
    invisible(combined)

  }

@@

```{r echo=F}
overdisp_fun <- function(model) {
  ## number of variance parameters in an n-by-n variance-covariance matrix
  vpars <- function(m) {
    nrow(m) * (nrow(m) + 1)/2
  }
  # The next two lines calculate the residual degrees of freedom
  model.df <- sum(sapply(VarCorr(model), vpars)) + length(fixef(model))
  rdf <- nrow(model.frame(model)) - model.df
  # extracts the Pearson residuals
  rp <- residuals(model, type = "pearson")
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  # Generates a p-value. If less than 0.05, the data are overdispersed.
  pval <- pchisq(Pearson.chisq, df = rdf, lower.tail = FALSE)
  c(chisq = Pearson.chisq, ratio = prat, rdf = rdf, p = pval)
}

residfit <- function (model, col="black") {
  f<-fitted(model)
  r<-resid(model, type='pearson')
  plot(f, r, col=col, main='Residuals vs. Fitted')
  L1<-loess(r~f)
  fvec = seq(min(f),max(f),length.out=1000)
  lines(fvec,predict(L1,fvec),col='red')
}

#do the same for the Scale-Location plot
scaleloc <- function(model,col="black") {
  f <- fitted(model)
  r <- sqrt(abs(residuals(model, type='pearson'))) #transformed pearson residuals
  plot(f,r,col=col, main='Scale-Location Plot') 
  L1 <- loess(r~f)
  fvec = seq(min(f),max(f),length.out=1000)
  lines(fvec,predict(L1,fvec),col=2)
}
```

@@

fdata$None.Myc <- as.factor(fdata$None.Myc)
fdata$Herbivory <- as.factor(fdata$Herbivory)
fdata$Mycorrhiza <- as.factor(fdata$Mycorrhiza)
fdata$Lesion <- as.factor(fdata$Lesion)
fdata$None.Herb <- as.factor(fdata$None.Herb)
fdata$None.Path <- as.factor(fdata$None.Path)
summary(fdata)
```
```{R gather dataframe}
length(unique(fdata$indiv2))
Cross<- data.frame(c(rep(1:100, times=225)))
fdatac <- cbind(fdata,Cross)
colnames(fdatac)[11]<-"cross"
fdatac %>% gather(Trait, Value, c(4,6,7)) -> fdata_gather # The warning is an inconsequential bug from tidyverse (https://github.com/tidyverse/tidyr/issues/386)
fdata_gather$Value<-as.numeric(fdata_gather$Value)
fdata_gather$Trait<-as.factor(fdata_gather$Trait)
fdata_gather <- fdata_gather[,-c(2:4)]
```

@@

ndata<-cbind(indiv,tdata)
ndata<-ndata[,-c(2,3,4,9,14,17:37)]
ndata$None.Path<-as.integer(ndata$None.Path)
ndata$Lesions<-as.integer(100-ndata$None.Path)
ndata$None.Myc<-as.integer(ndata$None.Myc)
ndata$Mycorrhiza<-as.integer(100-ndata$None.Myc)

@@

FloristicSurvey$Population<-as.factor(FloristicSurvey$Population) # Make the population a factor and not an interger
FloristicSurvey[is.na(FloristicSurvey)] <- 0
sum(row.has.na <- apply(FloristicSurvey, 1, function(x){any(is.na(x))}))
```

@@

@@

## finally plotting.
mult <- 1 #multiplier for the arrows and text for envfit below. You can change this and then rerun the plot command.
NMDS_of_Floristic_Composition<-ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, color=df_ell.FSurvey.GM_coverage$GM_coverage))+ 
    geom_point( aes(color = FloristicSurvey.NMDS.data$GM_Coverage), size = 1)+ 
    scale_color_manual(values = c(14,5,19,2))+ 
    coord_cartesian(xlim = c(-.5,.5))+
  theme_simple()+ guides(color=guide_legend("Garlic Mustard Coverage"))+
  ggtitle("NMDS of Floristic Composition \n in a Garlic Mustard Population")+
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_color_manual(values=c("green3"," blue3","orange3","red3"))
NMDS_of_Floristic_Composition
ggsave(file="NMDS_of_Floristic_Composition.eps", plot=NMDS_of_Floristic_Composition, width=10, height=8)
```

### RDA
species comp ~ GMcov * pop + soil characteristics inside and outside as covariates? 
```{r}

@@

# Redundancy analysis
sp.comp <- FloristicSurvey[,4:(length(FloristicSurvey)-1)]
var <- FloristicSurvey[,c(1:3,length(FloristicSurvey))]
var$Quadrat <- as.character(var$Quadrat)
for(i in 1:length(var$Quadrat))if(var$Population[i] == "7"){
  var$Quadrat[i]<-paste("7",var$Quadrat[i],sep="")
}else if(var$Population[i] == "3"){
  var$Quadrat[i]<-paste("3",var$Quadrat[i],sep="")
}else if(var$Population[i] == "14"){
  var$Quadrat[i]<-paste("14",var$Quadrat[i],sep="")
}else if(var$Population[i] == "13"){
  var$Quadrat[i]<-paste("13",var$Quadrat[i],sep="")
}else if(var$Population[i] == "1"){
  var$Quadrat[i]<-paste("1",var$Quadrat[i],sep="")
}

var$Population <- as.factor(var$Population)
var$GM_Coverage<-as.numeric(var$GM_Coverage)
sp.comp.hell<-decostand(sp.comp,method="hellinger")

formulaRDA <- rda(sp.comp.hell ~ GM_Coverage + Population , data=var)

head(summary(formulaRDA))
RsquareAdj(formulaRDA)
coef(formulaRDA)
scor = scores(formulaRDA, display=c("sp", "cn", "bp"), scaling=2)

anova.cca(formulaRDA,step=1000)
anova.cca(formulaRDA,by="terms", step=1000)

# numeric centroids
numeric_centroids <- data.frame(scor$centroids)
numeric_centroids
str(numeric_centroids)
numeric_centroids$Population <- rownames(numeric_centroids)
numeric_centroids

# testing it out
ggplot(numeric_centroids, aes(x = RDA1, y = RDA2))+
  geom_text(aes(label = Population))+ # label tells geom_text which text you want to plot
  ylim(-1,1)+ #NB note that this is a convenience wrapper and may cut data out of your plot
  xlim(-1,1) #important if you are calculating stats in the plot - these will be excluded

# species
species_centroids <- data.frame(scor$species)
species_centroids
species_centroids$species_names <- rownames(species_centroids) # you can also put label = rownames() etc in the ggplot code. But sometimes you may want it in a column for later

ggplot(numeric_centroids, aes(x = RDA1, y = RDA2))+
  geom_text(aes(label = Population))+
  geom_text(data = species_centroids, aes(label = species_names),
            colour = "orange")+
  ylim(-1,1)+
  xlim(-1,1)

# arrows
continuous_arrows <- data.frame(scor$biplot)
continuous_arrows
continuous_arrows$manure_class <- rownames(continuous_arrows) #turning rownames into a variable
continuous_arrows

site_scores <- data.frame(scores(formulaRDA)$sites)
site_scores$site_num <- var$Quadrat
site_scores$coverage<-var$GM_Coverage_category

RDA_plot <- ggplot(numeric_centroids, aes(x = RDA1, y = RDA2))+
   geom_point(data = site_scores, aes(x = RDA1, y = RDA2,  color=coverage),
             size = 3)+
   coord_cartesian(x = c(-1, 1), y = c(-1,1.2))+
   geom_segment(data = continuous_arrows,
                aes(x = 0, xend = mult * RDA1,
                    y = 0, yend = mult * RDA2),
                arrow = arrow(length = unit(0.25, "cm")), colour = "grey") + #grid is required for arrow to work.
   geom_text(data = continuous_arrows,
             aes(x= (mult + mult/10) * RDA1, y = (mult + mult/10) * RDA2, 
                 label = manure_class), 
             size = 5,
             hjust = 0.5)+
   geom_text(aes(label = Population))+ theme_bw()
RDA_plot
ggsave(file="RDA_plot.eps", plot=RDA_plot, width=10, height=8)

@@

@@

Agg_stability_plot<-ggplot(Soil_characteristics, aes(Location,Agg_stability,fill=Location))+ geom_boxplot() +
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_fill_manual(values=c("red3","blue3"))

ph_plot<-ggplot(Soil_characteristics, aes(Location,pH,fill=Location))+ geom_boxplot() +
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12)) + scale_fill_manual(values=c("red3","blue3"))

C_percent_plot<-ggplot(Soil_characteristics, aes(Location,C_percent,fill=Location))+ geom_boxplot() +
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12)) + scale_fill_manual(values=c("red3","blue3"))

N_percent_plot<-ggplot(Soil_characteristics, aes(Location,N_percent,fill=Location))+ geom_boxplot() +
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_fill_manual(values=c("red3","blue3"))

edaphic_soil_qualities_plot<-grid_arrange_shared_legend(Agg_stability_plot, ph_plot,C_percent_plot, N_percent_plot)
ggsave(file="edaphic_soil_qualities_plot.eps", plot=edaphic_soil_qualities_plot, width=10, height=8)

Soil_characteristics$Population<-as.factor(Soil_characteristics$Population)

GLMER_soil <- glmer(Location~scale(Agg_stability)*scale(C_percent)*scale(N_percent)+(1|Population),family=binomial(link='logit'),data=Soil_characteristics)
residfit(GLMER_soil)
scaleloc(GLMER_soil)

pr<-resid(GLMER_soil, type='pearson')
n<-nrow(Soil_characteristics)
c<-length(coef(GLMER_soil))
(Disp<-sum(pr^2)/(n-c))

summary(GLMER_soil)
options(na.action = "na.fail")
dredge(GLMER_soil) 
# A model with nothing is best...
```

LDA differs from RDA and CCA in that the response variable is a grouping of the
sites. This grouping may have been obtained by clustering the sites on the basis of
a data set, or it may represent an ecological hypothesis. LDA tries to determine to what extent an independent set of quantitative variables can explain this grouping.
```{r soil LDA}
var<-Soil_characteristics[,c(1,2)]
Y<-Soil_characteristics[,-c(1,2,5)]
var$Population<-as.factor(var$Population)
Location<-as.factor(var$Location)
Y$Sample <-paste(var$Population,var$Location) 
rownames(Y)<-Y$Sample
Y$Sample<-NULL

covar_cor = cor(Y)
corrplot.mixed(covar_cor, upper = "ellipse", lower = "number")

Nutrient_PCA<-dudi.pca(df = Y[, c(3, 4)], scannf = FALSE, nf = 1)
Nutrient_PCA$co
Nutrient_PCA$eig/sum(Nutrient_PCA$eig)
Y$Nutrient_PC1 = Nutrient_PCA$li[,1]

Y<-Y[,c(1,2,5)]

Y.d1 <-dist(Y)
Y.MHV<-betadisper(Y.d1,var$Location)
permutest(Y.MHV) # no significant difference in dispersion between groups

formulaLDA <- lda(var$Location ~ Agg_stability + Nutrient_PC1 + pH, data=Y)
summary(formulaLDA)
formulaLDA$means
scalvec<-data.frame(formulaLDA$scaling)
LDAval <- data.frame(predict(formulaLDA)$x)
anova(lm(LDAval$LD1~var$Location))
DF<-cbind(LDAval$LD1,data.frame(var$Location))
colnames(DF)<-c("LDAval","Location")
SoilLDAplot<-ggplot(DF, aes(LDAval, fill = Location)) + geom_density(alpha = 0.2)+
  ggtitle("Linear Discriminant analysis of Soil characteristics \n in and out of A. petiolata invasion")+
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_fill_manual(values=c("red3","blue3"))
SoilLDAplot
ggsave(file="SoilLDAplot.pdf", plot=SoilLDAplot, width=10, height=8)

@@

Myc_location_species_plot <- ggplot(fdat_ind,aes(loc,Mycorrhiza, fill=loc))+geom_boxplot()+facet_wrap(~species)+
  xlab("Plant Species")+ylab("Mycorrhizal \nColonization")+
  ggtitle("Species Mycorrhizal Colonization \n in and out of Garlic Mustard")+
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 18))+scale_fill_manual(values=c("light blue","forest green"))
Myc_location_species_plot
ggsave(file="Myc_location_species_plot.pdf", plot=Myc_location_species_plot, width=10, height=8)

Lesion_location_species_plot <- ggplot(fdat_ind,aes(loc,Lesion,fill=loc))+geom_boxplot()+facet_wrap(~species)+
  xlab("Plant Species")+ylab("Lesion")+
  ggtitle("Species Lesions \n in and out of Garlic Mustard")+
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 18))+scale_fill_manual(values=c("red3","blue3"))
Lesion_location_species_plot
ggsave(file="Lesion_location_species_plot.pdf", plot=Lesion_location_species_plot, width=10, height=8)

Myc_location_population_plot<-ggplot(fdat_ind,aes(loc,Mycorrhiza,fill=loc))+geom_boxplot()+facet_wrap(~pop)+
  xlab("Population")+ylab("Mycorrhizal \nColonization")+
  ggtitle("Mycorrhizal Colonization \n in and out of Garlic Mustard Population")+
  theme_bw()+
  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 18))+scale_fill_manual(values=c("red3","blue3"))
Myc_location_population_plot
ggsave(file="Myc_location_population_plot.pdf", plot=Myc_location_population_plot, width=10, height=8)
```
